

\documentclass[a4paper, oneside, final]{scrartcl} 

\usepackage{scrpage2} 
\usepackage{titlesec} 
\usepackage{marvosym} 
\usepackage{tabularx,colortbl} 
\usepackage{fontspec} 
\usepackage{multicol}

\title{CV for Jason McGillivray}
\author{Jason McGillivray}
\date {October 2016}

\defaultfontfeatures{Mapping=tex-text}
\setmainfont[BoldFont={AGaramondPro-Bold}] {Adobe Garamond Pro} % Main document font and bold font

\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule] % Section formatting

\pagestyle{scrheadings} % Print the headers and footers on all pages

\addtolength{\voffset}{-0.9in} 

\addtolength{\textheight}{5cm} 


\newcommand{\gray}{\rowcolor[gray]{.90}}

% FOOTER SECTION

\renewcommand{\headfont}{\normalfont\rmfamily\scshape} % Font settings for footer

\cofoot{
\addfontfeature{LetterSpace=20.0}\fontsize{12.5}{17}\selectfont % Letter spacing and font size

2309 Brunswick{\large\textperiodcentered} Halifax NS{\large\textperiodcentered} Canada B3K 2Z1\\ % Your mailing address
{\Large\Letter} McGillivray.Jason@gmail.com \ {\Large\Telefon} (902) 789 2470 % Your email address and phone number
}

\begin{document}

\begin{center} % Center everything in the document

% HEADER SECTION

{\addfontfeature{LetterSpace=20.0}\fontsize{20}{20}\selectfont\scshape Jason McGillivray} % Your name at the top

\vspace{.3cm} % Extra whitespace after the large name at the top

%    OBJECTIVE

\section{Objective}
Results-driven with 17 years of engineering and development experience looking to continue my career in the IT sector as a software developer.

%    SKILLS

\section{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Computer Languages & Perl, Python, Ruby, Java, C, C++, Bash, KSH, Powershell, jQuery, JS, SQL \\
Protocols \& Web APIs & RESTful Web-Services, SOAP\\
Databases & PostgreSQL, DB2, SQLite, Sybase, MySql, Microsoft SQL \\
Tools & Vi, Eclipse, Curl, Twiki, CPAN, DBArtisan, Ant, Ivy, Git, LaTeX\\
Operating Systems & Linux, Solaris, FreeBSD, OpenBSD, HP-UX, Windows, OS X\\
Languages & Bilingual English \& French\\
\end{tabular}

%    WORK EXPERIENCE

\section{Work Experience}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2009 --- Present}\\
\gray Employer & \textbf{NTT Data --- Morgan Stanley Mobile Computing} \hfill Halifax, NS\\
\gray Job Title & \textbf{Mobile Development Principal Consultant}\\
\gray Languages & \textbf{Perl, Python, Java, jQuery, MySQL, PostgreSQL, Sybase}\\
\gray Tech & \textbf{Linux, Windows, Blackberry Enterprise Server, MobileIron, MobileGuard, LDAP, ActiveDirectory, MQ}\\
& Working with the Mobile teams I wrote many interesting apps and processes below are a few:

\begin{itemize}
   \item \textbf{SMS Archiving}:  background scripts and processes for the Firms SMS archiving to comply with Legal and Compliance standards archiving millions of messages per month into our Zantaz vault.
   \item \textbf{MobileIron Drift}: web app that higlights the configuration differences between all the MobileIron system and application level configurations.
   \item \textbf{Helpdesk User Look-up}: web app for our help-desk to allows querying of the MI infra for user devices, phone numbers, application entitlements, enrollment and geographical regions over the span of our global deployments.
   \item \textbf{MobileRFB}: Ready for Business process automation, this web application replaces a manual process that takes the L2 Ops team several hours daily with a dashboard to the metrics it needs to track daily.
   \item \textbf{IMAD}: Immediate disablement for emergency terminations, this process goes through and disables a users mobile device, ldap information, windows / linux accounts, exchange mailboxes.
   \item \textbf{UMP}: Universal Mobile Provisioning reads the firms HR published stream for termination, lost or stolen device requests, and ushers them off to specialized "connectors" which each handle their own disabling using MQ's.
\end{itemize}
All my projects include wiki release documentation and support information along with production deployment instructions. Tasked with technical interviews for all new potential candidates.
\end{tabularx}



\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2007 --- 2009}\\
\gray Employer & \textbf{Keane Canada --- Morgan Stanley Remote Computing} \hfill Halifax, NS\\
\gray Job Title & \textbf{Mobile Engineering Principal Consultant}\\
\gray Languages & \textbf{Perl, Python, Ruby, Rails, Django, Java, Sybase, MSSQL, MySQL, PostgreSQL, Bash, KSH}\\
\gray Tech & \textbf{Linux, Solaris, Windows, MacOS, Blackberry Enterprise Server, LDAP, CVS, SVN}\\
& Designed a highly visible Ruby on Rails application for Morgan Stanley to allow transient employee's to reserve various internal resources ( hotel'ing desks, seats, workstations, meeting rooms ). Using agile development methodologies along with test driven development we completed the project in a very short time frame.
The secondary purpose of this project was to champion the Ruby language into one of the Firms approved languages as it was not fully approved at the time.

In this time I also created the Blackberry server reporting framework which allowed the creation of daily reports to be exported from the BES databases that were merged from all our regions worldwide.

I also wrote and maintained several web applications that were used extensively by our Ops team to manage the blackberry servers and devices.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2007}\\
\gray Employer & \textbf{Keane Canada --- Fidelity Investments} \hfill Halifax, NS\\
\gray Job Title & \textbf{Senior Java Consultant}\\
\gray Languages & \textbf{Java, Flex, ActionScript, XDoclet, Ant, Bash}\\
\gray Tech & \textbf{Redhat Linux, Windows, Oracle DB, CVS}\\
& Wrote a series of automation scripts using Java, Ant and Bash, to allow the automatic conversion of the teams Java back-end to be converted to ActionScript Objects (for use with Adobe Flex) for usage in the front-end application, saving considerable man hours.
Created a library of custom graphical components in Flex 2.0 for the team to use in building their applications.
Setup and maintained the teams source control server, and wrote documentation and taught classes on how to use source control in a team environment.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2007}\\
\gray Employer & \textbf{Keane Canada --- Center of Excellence} \hfill Halifax, NS\\
\gray Job Title & \textbf{LiveCycle Administrator / Programmer}\\
\gray Languages & \textbf{Java J2EE, LiveCycle, Flex, Flex Data Services, Ruby, Rails, PHP}\\
\gray Tech & \textbf{Linux, Jboss, JNDI, PDF, Subversion, NetBeans}\\
& Created a tech demo application that was shown off at the Acord conference in Flordia, where the application received a warm reception from the insurance agencies. The application bridged the workflow between various technologies using a J2EE backend / LiveCycle data services, aggregating data from multiple web services using a Flex front-end written with the Cairngorm MVC framework and generating PDF's.

Wrote documentation and taught classes on writing J2EE web-services, MVC design patterns, Unit testing, Source Control with Subversion, Test Driven Development, Ruby and Rails. These seminars convinced many other team leads to adopt some of the concepts within their respective teams and personal projects.
\end{tabularx}

\vspace{12pt}


\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2005 --- 2007}\\
\gray Employer & \textbf{Keane Canada --- Morgan Stanley Remote Computing} \hfill Halifax, NS\\
\gray Job Title & \textbf{Senior Engineering Consultant}\\
\gray Languages & \textbf{Bash, Ksh, Perl, Python, ASP, PHP}\\
\gray Tech & \textbf{Linux, Solaris, Windows, Juniper Routers, Cisco and Avaya Hardware, Autosys, VMS, AFS}\\
& Administered the firms remote computing border gateways and Juniper Internet Gateway Appliances, and acted as a liason to the vendors. Completed several upgrade migration paths for our twenty thousand remote computing users to our new infrastructure.

Wrote a suite of Perl scripts to automate the scanning of our appliances and server farms around the world for SNMP reporting. Generated MRTG reports and configuration files for all the remote computing infrastructure, dynamically loadable from a Sybase database view-able as a dashboard layout.

Implemented a Single-Sign On with our Juniper IVE's, WholeSecurity and SiteMinder to create a seamless passing of credentials to all internal applications from the remote computing infrastructure. Maintained all the Solaris boxes and WholeSecurity installations for the remote computing team.

Created a statistical analysis dashboard and parsing scripts used to monitor usage metrics for our Citrix gateway farms and other remote applications.

Created numerous run-books and documentation for each of the processes that I implemented.
\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2003 --- 2004}\\
\gray Employer & \textbf{Synchronicity Inc} \hfill Halifax, NS\\
\gray Job Title & \textbf{Lead Operating Systems Developer and Administrator}\\
\gray Languages & \textbf{Perl, PHP, Python, C, PostgreSQL}\\
\gray Tech & \textbf{Linux, Kernel Modules, VPN, Point to point Tunneling Protocol, NAS, Exim, SNORT}\\

& Working directly with the CEO of the company, I created a Linux Live-CD distribution with built in PPTP VPN server infrastructure.
Implemented our servers IDS systems using custom written SNORT rules, along with spam-assassin filtering for our Email servers and Clam-av scanning of attachments.
Designed an automated installation procedure for spinning up new server hardware and integrating it into our environment.
Setup automated penetration testing on our network and application levels to help mitigate the risk of breaches to our company servers.
Wrote all of our internal web administration framework that allowed us to configure our server farm and user databases.

\end{tabularx}

\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2002 --- 2003}\\
\gray Employer & \textbf{SG5 Innovation} \hfill Moncton, NB\\
\gray Job Title & \textbf{Lead Developer}\\
\gray Languages & \textbf{Perl, PHP, Python, C, C++, WxWindows, PostgreSQL, Flash}\\
\gray Tech & \textbf{Linux, FreeBSD, IPFW, IPTables, Firewalls, MacOS, CodeWarrior}\\

& Designed and implemented a secure B2B E-Commerce contract bidding website from concept to maturity.
Setup and administered all of the company's servers (web, firewalls, databases, load balancers, source control, dev and qa environments).
Managed a team of 6 junior programmers and mentored them with the concepts introduced by the challenges of building our application.

\end{tabularx}


\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2000 --- 2002}\\
\gray Employer & \textbf{Open-Source Directory} \hfill Moncton, NB\\
\gray Job Title & \textbf{Lead Developer / Administrator}\\
\gray Languages & \textbf{Perl, PHP, Python, C, MySQL, Mailman, Postfix, XML, PostgreSQL}\\
\gray Tech & \textbf{Linux, FreeBSD, IPFW, IPTables, Firewalls}\\

& Designed and implemented an online bazaar/showcase for open-source software, easily searchable by end users.
Setup and configured all our web-servers, load balancers, firewall and development machines with open-source software.
Created all of our backup utilities, and support tools.
Developed an XML-exportable database for data exchange between organizations.
Helped in the design process of the Open-Source Logo that's still in use today to represent open-source applications around the world.
\end{tabularx}


\vspace{12pt}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{1999 --- 2000}\\
\gray Employer & \textbf{Roswell Computer Books} \hfill Moncton, NB / Halifax , NS\\
\gray Job Title & \textbf{Lead Developer / Administrator}\\
\gray Languages & \textbf{Perl, PHP, Python, MySQL,  XML}\\
\gray Tech & \textbf{Linux, MySQL, Mailman, Postfix}\\

& Created an E-Commerce book marketplace for Roswell computer books that was used by both of their store locations (Moncton and Halifax).
This included an inventory system for each of the stores, and building up and automating the server infrastructure required to host the site.
\end{tabularx}

%    EDUCATION

\section{Education}

\begin{tabularx}{0.97\linewidth}{>{\raggedleft\scshape}p{2cm}X}
\gray Period & \textbf{2000-2002}\\
\gray Program & \textbf{Web Master}\\
\gray Institution & \textbf{Dal, University} \hfill Halifax, NS\\
%&

\end{tabularx}

%    REFERENCES

\section{References}

\begin{tabular}{ l c r @{} >{\bfseries}l @{\hspace{6ex}} l }
\gray Reference & {Elias Koutsoubis}  \\
\gray Position &  VP Mobile Engineering - Morgan Stanley\\
\gray {\Large\Telefon} & (917) 318-0990 \\
\gray {\Large\Letter} & elias.koutsoubis@morganstanley.com\\
\\
\gray Reference & {June Young}  \\
\gray Position &  Morgan Stanley Dev\\
\gray {\Large\Telefon} & (902) 441-4013 \\
\gray {\Large\Letter} & june.young@morganstanley.com\\
\\
\gray Reference & David Weinberg\\
\gray Position &  Morgan Stanley Dev\\
{\Large\Telefon} & (902) 497-2944\\
{\Large\Letter} & david.weinberg@morganstanley.com\\

\end{tabular}
\end{center}
\end{document}
